Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-18 bbbq_article.tex
All supmat figs have same style

See table \ref{tab:ncbi_counts} for an overview of all amounts.

% Label: tab:ncbi_counts
\input{ncbi_peregrine_results/ncbi_counts.tex}

>>>>

See tables \ref{tab:ncbi_counts_1} and tables \ref{tab:ncbi_counts_2}
for an overview of all amounts.
In table \ref{tab:ncbi_counts_1} one expects [RJCB: name these]
numbers to add up. 
The number of unique SNPs and unique gene names
does not add up for MAP and TMP,
as one SNP may work on multiple isoforms, some of which can be MAP
where others can be TMP.
The number of unique SNPs and unique gene names
does not add up for TMPs in TMH and TMP in soluble regions
as one SNP may work on multiple isoforms, some of which can be MAP
where others can be TMP, and some SNPs fall in a TMH, where others
are found in soluble regions
In table \ref{tab:ncbi_counts_2} one expects [RJCB: name these]
numbers to add up.

% Label: tab:ncbi_counts_1
\input{ncbi_peregrine_results/ncbi_counts_1.tex}

% Label: tab:ncbi_counts_2
\input{ncbi_peregrine_results/ncbi_counts_2.tex}

### 2021-03-18 ncbi_peregrine_results/ncbi_counts.tex
Move information from figures to table
All supmat figs have same style

\caption{\label{tab:ncbi_counts}Amounts. map = MAP = membrane associated protein. tmp = TMP = transmembrane protein. in\_tmh = in transmembrane helix (TMH) of TMP. in\_sol = in soluble region of TMP. perc\_tmh = percentage transmembrane helix (TMH). }
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r}
\hline
what & raw & all\_proteins & map & tmp & in\_tmh & in\_sol\\
\hline
Number of variations & 60931 & 37831 & 16623 & 21208 & 3803 & 17405\\
\hline
Number of unique variations & 60544 & 37630 & 16606 & 21024 & 3789 & 17235\\
\hline
Number of unique SNPs & NA & 9621 & 4219 & 6026 & 1140 & 4936\\
\hline
Number of unique gene names & 953 & 911 & 457 & 605 & 325 & 590\\
\hline
Number of unique protein names & 5163 & 4780 & 2227 & 2553 & 1280 & 2467\\
\hline
Percentage TMH & NA & 10 & 0 & 19 & 26 & 18\\
\hline
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:ncbi_counts}Amounts. raw = all variations, including DNA variations. all\_proteins = all proteins. map = MAP = membrane associated protein. tmp = TMP = transmembrane protein. in\_tmh = in transmembrane helix (TMH) of TMP. in\_sol = in soluble region of TMP. }
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r|r|r|r|r}
\hline
what & raw & all\_proteins & map & tmp & in\_tmh & in\_sol & single\_in\_tmh & single\_in\_sol & multi\_in\_tmh & multi\_in\_sol\\
\hline
Number of variations & 60931 & 37831 & 16623 & 21208 & 3803 & 17405 & 452 & 7734 & 3351 & 9671\\
\hline
Number of unique variations & 60544 & 37630 & 16606 & 21024 & 3789 & 17235 & 451 & 7733 & 3338 & 9502\\
\hline
Number of unique SNPs & NA & 9621 & 4219 & 6026 & 1140 & 4936 & 160 & 2393 & 994 & 2762\\
\hline
Number of unique gene names & 953 & 911 & 457 & 605 & 325 & 590 & 96 & 282 & 243 & 344\\
\hline
Number of unique protein names & 5163 & 4780 & 2227 & 2553 & 1280 & 2467 & 304 & 1032 & 976 & 1435\\
\hline
Percentage TMH & NA & 10 & 0 & 19 & 26 & 18 & 11 & 5 & 35 & 26\\
\hline
\end{tabular}
\end{table}
